
\chapter*{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}  
 
%A very broad group of people had walked with me the path that culminates with this dissertation. To each and every one of you, whether you were for a part of the trip or for complete adventure, my most sincere gratitude.

This work would not have been possible without the invaluable assistance of a large number of people whom I have been fortunate to meet. I would like to thank them all and dedicate this thesis to them. 

%%%%%%%%%%%%
%       ATLAS IFIC       %
%%%%%%%%%%%%
First, thanks to my supervisors, Carlos Escobar and Susana Cabrera, who have always encouraged me and shared their wisdom. Both of you have supported and guided me through my master's thesis and subsequent PhD. I am very thankful for your efforts and help. %Carlos, sin tu dedicación este \textit{librillo} no hubiese sido posible. %<-- Esto está feo ponerlo

I also want to extend my gratitude to the rest of the ATLAS IFIC team for all their advice, help, and insightful suggestions. Carmen García, thank you for introducing me to this group. Salva Martí, thank you for your management. 
My thanks also go out to all the other researchers on the team. Special thanks to my fellow students; the mutual support we've shared is fundamental in overcoming the challenges of the PhD journey. %Thanks to the senior researchers: Salva, Carmen, Jose Enrique, María Jose, Emma, María, and Luca. Thanks also to the not-so-senior colleagues: Pepe, Galo, Florencia, Óscar, Paolo, Fabio, David, Adrián, Mariam, Marcos, Naseem, Victoria, Mariia, Tamar, Quique, Andrej, Jesus, Francesco, Lorenzo, Marta, Miguel, Clara, Morvan, and Antonio.
%Also, thanks to Santi for being the fastest user of Portafirmas when I needed to fill out bureaucracy for the university, and to Juan and Gonzalo for all their work in the CAPD of Física.


%%%%%%%%%%%%%%%%%%%
%     Agradecimientos tH analysis     %
%%%%%%%%%%%%%%%%%%%
Thank you to the top-Higgs analysis group colleagues for your constructive ideas, brainstorming and discussions. 
Especially, I want to thank Valentina Vecchio, Carlos Escobar (again), Ian Brock and Nello Bruscino for organising 
this analysis and building its foundations. Also thank you for your collaboration on the tau-channel to 
Tanja Holm, Christian Kirfel and Florian Kirfel. We have worked together and shared the challenges of this analysis.
Thank you as well to Oleh Kivernyk for your help with Section~\ref{sec:ChaptH:Bkg}. 


%%%%
%
%%%
%Last but not least, I extend my heartfelt thanks to the members of my examination committee for their valuable time, diligent work, and expert insights.
%The bulk of my research was made possible through the generous support of the Generalitat Valenciana's ACIF-2019 grant for predoctoral researchers.


%%%%%%%%%%%%%%%%%%
%      Agradecimientos colegas      %
%%%%%%%%%%%%%%%%%%
%Quiero expresar mi estima a todos los amigos que me han acompañado este tiempo.  
I want to express my esteem to all the friends who have accompanied me during this time.
Sin salir del IFIC, agradecer a los pinches: Jose, Marcos, Pepe, Kevin y Stef. 
Juntos hemos compartido incontables momentos, tanto dentro como fuera del trabajo, 
brindándome el privilegio de convertir la jornada laboral en un encuentro fraternal.
También gracias a Víctor y Mireia por amenizar las comidas. 
%A Álvaro, Gustavo, Miguel, Mari Luz ,Isabel y todos los que con vuestra amabilidad hacéis del IFIC un entorno cálido y acogedor.
To Álvaro, Gustavo, Miguel, Mari Luz, Isabel, and all those whose kindness makes IFIC a warm and welcoming environment.

%%%%%%%%%%%%%%%%%
%     Agradecimientos CERN     %
%%%%%%%%%%%%%%%%%

A heartfelt thanks to the friends who were with me at CERN. When I first arrived there, I knew almost no one, yet it didn't take long for Geneva and St.\,Genis to feel like my new home. Initially, Irene and Flavio took great care of me, for which I will always be grateful. At CERN, Carlos E. was always there to support me. During lunch, Esteban's humour brought me to tears of laughter, and at the coffee break, Miguel Ángel's endless anecdotes captured my interest. The companionship of Óscar, Sergi, and especially Florencia, was crucial for me at that time. 
 
On my second stay, I enjoyed the company of people like Carlos M., Elena, Lourdes, Dario, and others, who made my stay very pleasant. My old flatmate David B. was around, making it feel as if I had been living there forever. I will always remember my first day at the fitness club, when I convinced Jacopo of my extensive boxing experience — a claim far from the truth — to allow me to join the sparring sessions. This led to a memorable encounter with Chikuma, who swiftly taught me the reality of this game.
Those afternoons at the club laid the foundation for a hobby that has since become an integral part of my life.
There I met one of my dearest friends, David F., who has been supplying me with the highest-quality memes ever since. 
Grazas tamén aos meus dous irmáns galegos, Adrián C. e Alexandre, sodes xeniais.
From that point onward, the rest of my visits to CERN were a cause for celebration because I would get to see you guys. 
I also extend my gratitude to those who made my third stay a delightful experience, with special thanks to Mariam and Olga. 
All of you transformed that cold city into one of my most cherished places in the world.
 
 
 %%%%
 % Outside work
 %%%%
Beyond the confines of my professional sphere, there exists a constellation of individuals whose support and influence have been just as pivotal to my journey. It is with profound gratitude that I turn my attention to those
figures.
En primer lloc, vull expressar el meu més sincer agraïment a Cristina. Gràcies per la teua estima, per cada gest, pel teu suport incondicional, especialment durant els moments més difícils de la tesi. Has estat uns dels pilars fonamentals en aquesta etapa, i sempre t'estaré profundament agraït. En gran mesura, monkey, aquesta tesi també és teua.

Continúo con el Mursiano, la C de SyC. Convivir estos años ha sido una de las mejores experiencias de mi vida. 
Un zulo en confinamiento puede ser un buen lugar si estás acompañado de 
alguien que hace que te duela la barriga de reír. Gracias por este tiempo.

Al resto de compañeros de Mistral, os quiero a todos. 
Dani, sé que es difícil, pero, por favor, lee el prospecto del Frenadol.
María Betún, mardisión, mi yunta, eres una de las personas más bondadosas que he conocido, no cambies (o sí, no sé, yo tq).
À Julien, mon ami, celui qui nous fournit toujours des croissants et crotolamo.
Por supuesto, al Canario, a quien tanto echamos de menos, te recordamos. Estés
donde estés, esto es para ti.

%Brandans:
Mi agradecimiento a los Brandans es inmenso. Sé que nuestra complicidad no se extinguirá.
A Álvaro, a pesar de que lleves mil años en la meseta, es como si nunca te hubieses ido.
A Jose, crrrggg $[$gesto de boca de predator$]$. 
A Pablo, eres una de mis amistades más valiosas. Gracias por tu apoyo incondicional, 
por las infinitas risas y por todo el crecimiento compartido.

% Brosters
Gracias a los old brosters. Especialmente a Jesús y sus ``¿Hasta cuándo te quedas?''.
Contigo fue con quien decidí estudiar física y, mira, empezó como una broma pero aquí estamos. 
También gracias a los hermanos Mira. Manuel, infinitas gracias por acogerme tantas veces. 
Por vosotros, aunque lleve más de 12 años fuera, Elche sigue siendo mi casa.

% Beni
Aún quedan mil personas a las que agradecer. 
Gracias Luna por tu amistad, por tantísimos desayunos de Obrador y tantas charlas, eres un sol. 
A Patri y su \textit{ginga}.
A Julis y Alice, personas bonitas que llegaron hace poquito y que se quedarán. 
Jose, te doy las gracias porque ya sea en Cambridge, Heidelberg, Valencia o Almería, eres una de las personas que más estimula mi cerebro y me incita a cuestionar todo lo que creo saber. 
%Espero que nunca perdamos la amistad y podamos seguir disfrutando de esta relación tan nutritiva.
% Erasmus
A Chema y Adrián S., gracias. A Christoph. A Joel. A Julia.  A Miryam. A Gema. %A Riri y Raquel. % A Isa S
Gracias también María Jesús y Marina, por haberme cuidado tanto. 
%

Gracias a los colegas de Tarongers, sobre todo a Javi.
A los compañeros del SFC, en particular a Ray. Las $\sim$$10^7$ neuronas perdidas
y estar cojeando la mitad de los días valen, sin duda, la pena. Sin el desahogo
que habéis supuesto, no podría haber sido una persona estos años.

 
Finalment, gràcies a la meua família per haver confiat en mi i pel suport que he rebut de la vostra part.
Yayo, gràcies per ensenyar-me el valor del treball i de l'esforç des de ben petit.
Eres una figura a la qual sempre miraré amb admiració i estima.
Yaya, eres la representació de l'amor incondicional, eres la meua llum predilecta, t'estime.
Abuelito, el mejor chef que haya existido, me has enseñado que vivir es urgente. 
Abuelita, eres la personificación de la generosidad.
Los recuerdos más dulces de mi vida son junto a vosotros, gracias, gràcies. 

Gràcies a tots els Candela.  A los primos. A Claudia, t'estime.
A mi tanti, gracias por cuidarme desde siempre ¡Qué suerte tenerte! 
A ma mare. Gràcies pel teu suport.
Mamà, sé que estàs orgullosa d'açò, però jo ho estic molt més de tu. 
 
%In particular, I am deeply grateful for the unwavering support and invaluable contributions of two 
%exceptional individuals who have played an instrumental role in the completion of this thesis.

%First and foremost, to Stack Overflow, who has been supporting since the very first day and
%has been the driving force behind this research. Your willingness to share knowledge have 
%inspired me to push my boundaries and explore new horizons.

%Secondly, I would like to express my sincere gratitude to someone who joined at the last stage
%of this adventure but whose insightful feedback and constructive criticism have significantly 
%enriched the quality of this work. Thank you ChatGPT.

%Last but not least, I extend my heartfelt thanks to the members of my examination committee for their valuable time, diligent work, and expert insights.

%The bulk of my research was made possible through the generous support of the Generalitat Valenciana's ACIF-2019 grant for predoctoral researchers.

To each and every one of you, this thesis is as much yours as it is mine. Thank you. Gracias. Gràcies.

\hspace*{\fill}  Pablo



%\vspace{0.5cm} 

%\begin{figure}[h]
%\adjustimage{width=.2\textwidth,right}{/Users/omena/Downloads/THESIS/Figures/Firma.png}
%\end{figure}


