%PREAMBLE
\begin{comment}
%\documentclass[11pt]{article}
%\input{latex/mycommands.tex}
%\begin{document}
%ENDPREAMBLE
\end{comment}


\chapter{Probing the top-quark polarisation in the single-top \tchannel production}
\label{chap:Polarisation}
%{\LARGE \textbf{}\\}

%\tableofcontents
% Everything is in the glance entry: 
	The polarisation paper: \url{https://atlas-glance.cern.ch/atlas/analysis/papers/details.php?id=13286}
	%https://cds.cern.ch/record/2293245/files/CERN-THESIS-2017-238.pdf


%%%%%%%%%%%%%%%%%%%%%%%
%         Introduction to polarisation                 %
%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{chap:Polarisation:Intro}
Apart from the studies of the associated production of a top quark and a Higgs boson, in this thesis
is also presented a simultaneous measurement of the three components of the top-quark and top-antiquark polarisation
vectors in \tchan$\,$single-top-quark production.

The single-top-quark production and decay via the \Wtb vertex, provides a unique way to study
the coupling between the top-quark, the \PW boson and the \Pbottom quarks. This vertex is studied
through the measurement of the polarisation observables for events produced in $\Pproton \Pproton$ collisions.




Importance of signal selection: In the polarisation analysis we look at angular distributions. 
The use of a BDT or NN as it is done on the \tHq studies can introduce bias on this angular distribution.
This studies are extremely  sensible to any bias introduced on the angular distributions, therefore a cut-and-count method for the signal selection
is the preferred option.

% The polarisation analysis presents three results:
%     - Measures the rhree components of the top-quark and the top-antiquark polarisation vectors
%     - Differential measurement
%     - EFT interpretation of the differential measurement
% The followup study is the 4-angle analysis, in which the helicity is also measured in the t-channel. This allows to put numbers to more EFT aparametrs

%%%%%%%%%%%%%%%%%%%%%%%
%                    Polarisation 	                    %
%%%%%%%%%%%%%%%%%%%%%%%
\section{Top quark polarisation observables}
\label{chap:Polarisation:Observable}


%%%%%%%%%%%%%%%%%%%%%%%
%         Simulated event samples                   %
%%%%%%%%%%%%%%%%%%%%%%%
\section{Simulated event samples}
\label{chap:Polarisation:MC}

%%%%%%%%%%%%%%%%%%%%%%%%
%              Object reconstruction                     %
%%%%%%%%%%%%%%%%%%%%%%%%
\section{Object reconstruction}
\label{chap:Polarisation:Object}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%            Trigger requirements and event preselection              %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Trigger requirements and event preselection}
\label{chap:Polarisation:TriggerPR}


%%%%%%%%%%%%%%%%%%%%%
%            Top quark recontruction            %
%%%%%%%%%%%%%%%%%%%%%
\section{Top quark reconstruction}
\label{chap:Polarisation:Topreco}
A precise determination of the top quark 4-momentum is crucial to perform the polarisation measurements.
If this is not done appropriately, the angular variables can not be properly obtained and the sensibility of
the analysis is consequently reduced.
The top quark is reconstructed using a kinematic likelihood fit (KLFIT) \cite{Erdmann_2014}
%slide 11/22 https://indico.cern.ch/event/1139204/contributions/4850084/attachments/2437000/4174393/valencia_top.pdf


%POSTAMBLE
\begin{comment}

\bibliographystyle{../../jhep}
\bibliography{../../biblio}

\end{document}

%ENDPOSTAMBLE
\end{comment}
